---
title: "Lecture 5 - Linear models with tidymodels"
subtitle: "Impact of Outliers 😲"
output:
  html_document:
    number_sections: true
    fig_caption: true
    toc: true
    fig_width: 5
    fig_height: 4
    theme: cosmo
    highlight: tango
    code_folding: show
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      fig.align = "center")
```


# Preparations {.tabset .tabset-fade}

## Libraries

```{r load_lib, message=FALSE, warning=FALSE, results='hide'}
library(tidymodels)
library(tidyverse)
library(magrittr)
library(skimr)
library(knitr)
theme_set(theme_bw())
```

## Data load

```{r}
file_path <- "../competition/House Prices - Advanced Regression Techniques/input/house-prices-advanced-regression-techniques/"
files <- list.files(file_path)
files
```

```{r, message=FALSE}
train <- read_csv(file.path(file_path, "train.csv")) %>% 
  janitor::clean_names()
test <- read_csv(file.path(file_path, "test.csv")) %>% 
  janitor::clean_names()
```


# Data overview

## Basic info.

```{r}
dim(train)
dim(test)
```

## Distribution of `sale_price`

```{r message=FALSE, class.source = 'fold-hide'}
train %>% 
  ggplot(aes(x = log(sale_price))) +
  geom_histogram()
```

# Outliers {.tabset .tabset-fade}

## gr_liv_area variable

* Any thoughts about right 4 points?

```{r class.source = 'fold-hide'}
train %>% 
  ggplot(aes(x = gr_liv_area, 
             y = log(sale_price))) +
  geom_point(alpha = 0.6) +
  labs(title = "Before removing outliers")
```

```{r}
# outliers 
train %>%
  filter(gr_liv_area > 4500) %>%
  DT::datatable(width = "100%",  
                options = list(scrollX = TRUE))

# outliers remove
train %<>% filter(!(gr_liv_area > 4500))
```

```{r class.source = 'fold-hide'}
train %>% 
  ggplot(aes(x = gr_liv_area, 
             y = log(sale_price))) +
  geom_point(alpha = 0.6) +
  labs(title = "After removing outliers")
```

## total_bsmt_sf variable

```{r class.source = 'fold-hide'}
train %>% 
  ggplot(aes(x = total_bsmt_sf, 
             y = log(sale_price))) +
  geom_point(alpha = 0.6) +
  labs(title = "Before removing outliers")
```

```{r}
# outliers 
train %>%
  filter(total_bsmt_sf > 3000 &
                   log(sale_price) < 13) %>%
  DT::datatable(width = "100%",  
                options = list(scrollX = TRUE))

# outliers remove
train %<>% filter(!(total_bsmt_sf > 3000 &
                   log(sale_price) < 13))
```

```{r class.source = 'fold-hide'}
train %>% 
  ggplot(aes(x = total_bsmt_sf, 
             y = log(sale_price))) +
  geom_point() +
  labs(title = "After removing outliers")
```

## garage_area variable

```{r class.source = 'fold-hide'}
train %>% 
  ggplot(aes(x = garage_area, 
             y = log(sale_price))) +
  geom_point(alpha = 0.6) +
  labs(title = "Before removing outliers")
```

* Outliers

```{r}
# outliers 
train %>% 
  filter(garage_area > 1230) %>%
  DT::datatable(width = "100%",  
                options = list(scrollX = TRUE))

# outliers remove
train %<>% filter(garage_area <= 1230)
```

```{r class.source = 'fold-hide'}
train %>% 
  ggplot(aes(x = garage_area, 
             y = log(sale_price))) +
  geom_point() +
  labs(title = "After removing outliers")
```

# Preprecessing with `recipe`

## `all_data` combine and name cleaning with `janitor`

```{r}
all_data <- bind_rows(train, test)
names(all_data)[1:10]
```

## Make recipe

```{r}
housing_recipe <- all_data %>% 
  recipe(sale_price ~ .) %>%
  step_rm(id) %>% 
  step_log(sale_price) %>%
  step_modeimpute(all_nominal()) %>% 
  step_dummy(all_nominal()) %>% 
  step_meanimpute(all_predictors()) %>%
  step_normalize(all_predictors()) %>% 
  prep(training = all_data)

print(housing_recipe)
```

## `juice` the all_data2 and split

```{r}
all_data2 <- juice(housing_recipe)
```

We are done for preprocessing. Let's split the data set.

```{r}
train_index <- seq_len(nrow(train))
train2 <- all_data2[train_index,]
test2 <- all_data2[-train_index,]
```

# Split the train into validation and train

```{r}
set.seed(2021)

# validation_split <- validation_split(train2, prop = 0.7)
validation_split <- vfold_cv(train2, v = 10, strata = sale_price)

# actual split id stored in the following
# validation_split$splits[[1]]$in_id
# the whole point is that it's there and trust tidymodels :)
# head(validation_split$splits[[1]]$in_id)
```

# Set the tuning spec

```{r}
tune_spec <- linear_reg(penalty = tune(),
                        mixture = tune()) %>%
  set_engine("glmnet")

param_grid <- grid_regular(penalty(), 
                            mixture(),
                            levels = list(penalty = 100,
                                          mixture = 10))
```

# Set workflow()

```{r}
workflow <- workflow() %>%
  add_model(tune_spec) %>% 
  add_formula(sale_price ~ .)
```


# Tuning $\lambda$ and $\alpha$

Elestic net uses the loss function as follows;

$$\underset{\beta}{min}\left(y-X\beta\right)^{T}\left(y-X\beta\right)+\frac{\lambda}{2}\left(\alpha\left\Vert \beta\right\Vert _{1}+\left(1-\alpha\right)\left\Vert \beta\right\Vert _{2}^{2}\right)$$

This can be thought of as the mixture of the Lasso and Ridge regression loss function. $\lambda$ is related to penalty, $\alpha$ is related to the proportion of Lasso penalty in the loss function.

```{r}
library(tictoc)
doParallel::registerDoParallel()

tic()
tune_result <- workflow %>% 
  tune_grid(validation_split,
            grid = param_grid,
            metrics = metric_set(rmse))
toc()
```

```{r}
tune_result %>% 
  collect_metrics()
```

# Visualization of the tunning result

```{r}
tune_best <- tune_result %>% select_best(metric = "rmse")
tune_best$penalty
tune_best$mixture
```


```{r message=FALSE}
tune_result %>%
  collect_metrics() %>%
  filter(mixture == tune_best$mixture) %>% 
  ggplot(aes(penalty, mean, color = .metric)) +
  geom_line(size = 1.5) +
  scale_x_log10() +
  theme(legend.position = "none") +
  labs(title = "RMSE")
```

```{r}
tune_result %>% show_best()
```

# Set Elastic net regression model and fitting

`mixture` parameter determines the proportion of Lasso regression in the Elastic net.

```{r message=FALSE, warning=FALSE}
elastic_model <- 
    linear_reg(penalty = tune_best$penalty,
               mixture = tune_best$mixture) %>%
    set_engine("glmnet")

elastic_fit <- 
    elastic_model %>% 
    fit(sale_price ~ ., data = train2)

options(max.print = 10)
elastic_fit %>% 
    tidy() %>% 
    filter(estimate > 0.001)
```

# Prediction and submit

```{r warning=FALSE}
result <- predict(elastic_fit, test2)
result %>% head()
```

```{r}
submission <- read_csv(file.path(file_path, "sample_submission.csv"))
submission$SalePrice <- exp(result$.pred)
write.csv(submission, row.names = FALSE,
          "lecture5-2.csv")
```
