---
title: "Homework 2 - Generalized Linear Models"
author: "Due on 2021-05-14"
date: ""
# documentclass: oblivoir
# XeTeXinputencoding: korean
# XeTeXdefaultencoding: korean
output: 
    bookdown::pdf_document2:
        latex_engine: xelatex
        toc: FALSE
urlcolor: blue
header-includes: |
    \usepackage{bbold}
# mainfont: NanumMyeongjo
# monofont: NanumGothicCoding
# \usepackage[hangul]{kotex}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(dev = "cairo_pdf")
knitr::opts_chunk$set(fig.showtext=TRUE)
```

# Notice {-}

 - All homework should be turned in pdf format **using Rmarkdown**.
 - Homework can be written in Korean.

# Exponential family

When a random variable $Y$ belongs to exponential family, then the pdf of the random variable can be written as following form:

$$f_{Y}\left(y;\theta,\phi\right)=exp\left[\frac{y\theta-b\left(\theta\right)}{a\left(\phi\right)}+c\left(y,\phi\right)\right]$$

where $a, b, c$ are functions, and the parameter $\theta$ is often referred to as **canonical parameter**.

1) Express the p.d.f of random variable $Y$
$$Y \sim Bernulli\left(p\right)$$
in the above form, which follows the Bernulli $p$:
$$f_{Y}\left(y;p\right)=p^{y}\left(1-p\right)^{1-y}\mathbb{1}_{\left(y\in\{0,1\}\right)}$$

2) Express the p.d.f of random variable $Y$
$$Y\sim Poisson\left(\lambda\right)$$
in the above form, which follows the Poisson $\lambda$:
$$f_{Y}\left(y;\lambda\right)=\frac{\lambda^{y}e^{-\lambda}}{y!}\mathbb{1}_{\left(y\in\mathbb{Z^{+}}\right)}$$

3) We have learned that the link function in GLM is a function $g$ which connects the linear components with the $\mu=\mathbb{E}[Y]$. If link function $g$ satisfies the following condition, then $g$ is called a *canonical link function*.
$$\theta = g(\mu)$$
Verify the logit link for the logistic regression  and the log link for the poisson regression are the canonical link functions.

# Maximum Likelihood Estimator of Poisson Regression

```{r tab1, echo=FALSE}
example_data <- tibble::tribble(
    ~Policy, ~Policy.Years, ~Gender, ~Territory, ~Claims,
         1L,            5L,     "M",     "East",      0L,
         2L,            5L,     "F",     "East",      0L,
         3L,            4L,     "M",     "East",      1L,
         4L,            3L,     "F",     "West",      1L,
         5L,            4L,     "F",     "East",      0L,
         6L,            3L,     "F",     "West",      1L,
         7L,            5L,     "M",     "West",      0L,
         8L,            5L,     "M",     "West",      2L,
         9L,            3L,     "M",     "East",      1L,
        10L,            2L,     "F",     "East",      1L,
        11L,            4L,     "M",     "West",      1L,
        12L,            5L,     "F",     "West",      0L
    )

knitr::kable(example_data, 
             col.names = colnames(example_data),
             caption = "Example data for Problem 2",
             align = "ccccc", booktab = TRUE)
```

Save Table \@ref(tab:tab1) into `example_data` and do the Poisson regression using `Gender` over `Claims` as follows:

1) Calculate the coefficients by using the following code.

```{r eval=FALSE}
glm(Claims ~ Gender + Territory,
family = poisson(link=log), data = example_data)
```

2) Find the coefficients of Poisson regression above using an user define `R` function via gradient descent algorithm. Your answer must include the following steps:

    - Define Likelihood and Loglikelihood function

    - Calculate gradient of Loglikelihood function with repect to $\beta$.